\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}

### 2016-11-21 paper.tex
...

In this paper, we focus on the online scenario where a provider intends to select participants to perform sensing tasks and provide them with some rewards under a budget constraint. The objective of the problem is to maximize the total values of selected participants considering the time-discounting properties, while at the same time achieve budget feasibility and strategy-proofness. Taking the budget constraint into account brings another challenge in designing a strategy-proof mechanism, since existing budget feasible mechanism design approaches(\eg, \cite{singer2010budget, chen2011approximability,Bei:2012:BFM:2213977.2214020,Chen:2011:ABF:2133036.2133090}) are not practical in scenarios where participants' values are time-discounting.

@@

\item We think about two cases according to the value function. The value function in these two cases is additive and submodular, the latter is more general.
\end{itemize}
\subsection{Paper Organization}
The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VI.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

When $\epsilon$ is sufficiently small, we can always find such a parameter $\lambda$ equals $2\left(\frac{U}{L}\right)^{l-1}$. Then the expected competitive ratio is:
\begin{align}
\left(\frac{U}{L}\right)^{2-2l}\frac{U}{16(U+L)}(1-\frac{1}{e}). 
\end{align}
\end{proof}
% Due to limitations of space, we omit the proof here.
%\begin{equation}
%\left\{
%\begin{aligned}
%\frac{\left(\frac{U}{L}\right)^{l-1}}{\lambda}<\frac{1}{2}\\
%\lambda < \frac{\left(\frac{U}{L}\right)^{l-2}}{\epsilon}\\
%\end{aligned}
%\right.
%\end{equation}
\section{Mechanism with Monotone Submodular Value Function}
In this section, we propose an online mechanism, which is named as TDMS, for the general model.
\subsection{System Model}
The general model is similar with the model we have presented in section III. However the task is divided into some sub-tasks and the bid of each participant includes the set of sub-tasks she can finish. The bid of of participant $i$ is $\theta_i=(a_i,d_i,p_i,c_i)$, where we use the same notation $p_i$ to represent the sub-task set of participant $p_i$ for brevity.
\subsection{Mechanism Design}
In last section, we propose an incentive mechanism for online crowdsensing with time-discounting values, specifically the total obtained value is linear summeration of value contributed by each participant, \ie,
%\begin{small}
\begin{equation}
V=\sum\limits_{i \in \mathbb{S}}v_i(t_i)
\end{equation}
%\end{small}
However in many scenarios~\cite{zhao2014crowdsource}, the value of participants to the platform is $f(\mathbb{S})$, where $f$ is a monotone submodular function ans $\mathbb{S}$ is the selected participants set. Particularly, we have solved the case where the value function $f(\mathbb{S})=\sum\limits_{i \in \mathbb{S}}v_i(t_i)$. Here we give the definition of monotone submodular function.
\begin{definition}[Monotone Submodular Function]
A function $f:2^{[n]}\to \mathbb{R}$ is submodular if and only if:
\begin{equation}
f(\mathbb{A}\cup\{i\})-f(\mathbb{A})\ge f(\mathbb{B}\cup \{i\})-f(\mathbb{B}). \forall \mathbb{A}\subseteq\mathbb{B} \notag
\end{equation}
\end{definition}
In existing works focused on submodular function maximation in the realm of incentive mechanism design for crowdsensing, the marginal value contributed by a participant is related to the order she is selected. Besides, the total value is only decided by the tasks of the selected participants. However in this paper, considering the time-discounting property, the value function is a bit more complicated. We still use the notation $f$ to denote the value function without considering time-discounting value. When a participant $i$ is selected at time $t_i$, her marginal contribution given a subset $\mathbb{S}$ is $f_{i|\mathbb{S}}=(f(\mathbb{S}\cup\{i\})-f(\mathbb{S}))\times\beta ^{-t_i}$.
Assume the selected participant set is $\{i_1,i_2,...,i_n\}$ and their selected time is $t_{i_1},t_{i_2},...,t_{i_n}$ respectively. So when select the first participant $i_1$, her real contribution value is $f_{t_{i_1}}(\{i_1\})=f(\{i_1\})\times \beta^{-t_{i_1}}$. The value contributed by the secondly selected participant without consider time-discounting property is $f(\{i_1,i_2\})-f(\{i_1\})$ and her true contribution should be discounted by timing $\beta^{t_{i_2}}$. Thus, the total value contributed these two participants is $f_{t_{i_1},t_{i_2}}(\{i_1,i_2\}) = f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}}$. We use $\tilde{f}$ to substitute $f$ when considering time-discounting property. So, the total value contributed by all these $n$ participants are
\begin{align}
&\tilde{f}(\{i_1,i_2,...,i_n\}) = f_{t_{i_1},t_{i_2},...,t_{i_n}}(\{i_1,i_2,...,i_n\}) \notag \\
&=f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}} \notag\\
&+... +[f(\{i_1,i_2,...,i_{n}\})-f(\{i_1,i_2,...,i_{n-1}\})]\times\beta^{-t_{i_n}} 
\end{align}

@@

\subsection{Mechanism Analysis}
\begin{theorem}
The mechanism with submodular value function is computationally efficient and budget feasible.
\end{theorem}
\begin{proof}
The proof is similar to the proof of theorem 2 and theorem 4.
\end{proof}
\begin{theorem}
The mechanism with submodular value function is time-truthful.
\end{theorem}
\begin{proof}
We prove that a participant can not obtain higher utility by misreporting her arrival or departure time. Denote her true arrival and departure time is $a_i, d_i$ and the misreporting time is $\hat{a}_i$ and $\hat{d}_i$. Fix the bids of all participants but $i$, we consider two cases.

@@

\textbf{case 2}: Participant $i$ can be selected when she departs and she misreports a cost $b_i$. If she still can not win the auction until she departs, she will get a payment equals $\frac{\tilde{f}^i_t(\mathbb{S}\backslash\{i\})}{\rho}$, which is the same as she bids truthfully because this payment has nothing to do with the bid. Otherwise, we assume she can win the auction at some time $t$ by misreporting lower cost(Apparently, higher cost doesn't "help"). The participant's failure is due to two reasons: low efficiency or budget constraint. If it is because of the budget, she will still fails. If it is because the low efficiency, \ie, $\frac{\tilde{f}^i_t(\mathbb{S})}{c_i}\ge\rho$, we can derive $c_i \ge \frac{\tilde{f}^i_t(\mathbb{S})}{\rho}$. If she wins the auction and get a payment, this payment will be less than her cost. So we have proved this case.

>>>>

In this paper, we focus on the online scenario where a provider intends to select participants to perform sensing tasks and provide them with some rewards under a budget constraint. The objective of the problem is to maximize the total values of selected participants considering the time-discounting properties, while at the same time achieve budget feasibility and strategy-proofness. Taking the budget constraint into account brings another challenge in designing a strategy-proof mechanism, since existing budget feasible mechanism design approaches (\eg, \cite{singer2010budget, chen2011approximability,Bei:2012:BFM:2213977.2214020,Chen:2011:ABF:2133036.2133090}) are not practical in scenarios where participants' values are time-discounting.

@@

\item We think about two cases according to the value function. The value function in these two cases is linear additive and submodular, the latter is more general.
\end{itemize}
\subsection{Paper Organization}
The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VI.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

When $\epsilon$ is sufficiently small, we can always find such a parameter $\lambda$ equals $2\left(\frac{U}{L}\right)^{l-1}$. Then the expected competitive ratio is:
\begin{align}
\left(\frac{U}{L}\right)^{2-2l}\frac{U}{16(U+L)}(1-\frac{1}{e}). 
\end{align}
\end{proof}
% Due to limitations of space, we omit the proof here.
%\begin{equation}
%\left\{
%\begin{aligned}
%\frac{\left(\frac{U}{L}\right)^{l-1}}{\lambda}<\frac{1}{2}\\
%\lambda < \frac{\left(\frac{U}{L}\right)^{l-2}}{\epsilon}\\
%\end{aligned}
%\right.
%\end{equation}
\section{Mechanism with Monotone Submodular Value Function}
In this section, we propose an online mechanism, which is named as TDMS, for the general model.
\subsection{System Model}
The general model is similar with the model we have presented in section III. However the task is divided into some sub-tasks and the bid of each participant includes the set of sub-tasks she can finish. The bid of of participant $i$ is $\theta_i=(a_i,d_i,p_i,c_i)$, where we use the same notation $p_i$ to represent the sub-task set of participant $p_i$ for brevity.
\subsection{Mechanism Design}
In last section, we propose an incentive mechanism for online crowdsensing with time-discounting values, specifically the total obtained value is linear summeration of value contributed by each participant, \ie,
%\begin{small}
\begin{equation}
V=\sum\limits_{i \in \mathbb{S}}v_i(t_i)
\end{equation}
%\end{small}
However in many scenarios~\cite{zhao2014crowdsource}, the value of participants to the platform is $f(\mathbb{S})$, where $f$ is a monotone submodular function ans $\mathbb{S}$ is the selected participants set. Particularly, we have solved the case where the value function $f(\mathbb{S})=\sum\limits_{i \in \mathbb{S}}v_i(t_i)$. Here we give the definition of monotone submodular function.
\begin{definition}[Monotone Submodular Function]
A function $f:2^{[n]}\to \mathbb{R}$ is submodular if and only if:
\begin{equation}
f(\mathbb{A}\cup\{i\})-f(\mathbb{A})\ge f(\mathbb{B}\cup \{i\})-f(\mathbb{B}). \quad \forall \mathbb{A}\subseteq\mathbb{B} \notag
\end{equation}
\end{definition}
In existing works focused on submodular function maximation in the realm of incentive mechanism design for crowdsensing, the marginal value contributed by a participant is related to the order she is selected. Besides, the total value is only decided by the tasks of the selected participants. However in this paper, considering the time-discounting property, the value function is a bit more complicated. We still use the notation $f$ to denote the value function without considering time-discounting value. When a participant $i$ is selected at time $t_i$, her marginal contribution given a subset $\mathbb{S}$ is $f_{i|\mathbb{S}}=(f(\mathbb{S}\cup\{i\})-f(\mathbb{S}))\times\beta ^{-t_i}$.
Assume the selected participant set is $\{i_1,i_2,...,i_n\}$ and their selected time is $t_{i_1},t_{i_2},...,t_{i_n}$ respectively. So when selecting the first participant $i_1$, her real contribution value is $f_{t_{i_1}}(\{i_1\})=f(\{i_1\})\times \beta^{-t_{i_1}}$. The value contributed by the secondly selected participant without consider time-discounting property is $f(\{i_1,i_2\})-f(\{i_1\})$ and her true contribution should be discounted by timing $\beta^{t_{i_2}}$. Thus, the total value contributed these two participants is $f_{t_{i_1},t_{i_2}}(\{i_1,i_2\}) = f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}}$. We use $\tilde{f}$ to substitute $f$ when considering time-discounting property. So, the total value contributed by all these $n$ participants are
\begin{align}
&\tilde{f}(\{i_1,i_2,...,i_n\}) = f_{t_{i_1},t_{i_2},...,t_{i_n}}(\{i_1,i_2,...,i_n\}) \notag \\
&=f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}} \notag\\
&+... +[f(\{i_1,i_2,...,i_{n}\})-f(\{i_1,i_2,...,i_{n-1}\})]\times\beta^{-t_{i_n}} 
\end{align}

@@

\subsection{Mechanism Analysis}
\begin{theorem}
The mechanism with submodular value function is computationally efficient and budget feasible.
\end{theorem}
\begin{proof}
The proof is similar to the proof of theorem 2 and theorem 4. So we omit it here.
\end{proof}
\begin{theorem}
The mechanism with submodular value function is time-truthful.
\end{theorem}
\begin{proof}
We prove that a participant can not obtain higher utility by misreporting her arrival or departure time. Denote her true arrival and departure time is $a_i, d_i$ and the misreporting time is $\hat{a}_i$ and $\hat{d}_i$. Fix the bids of all participants but $i$, we consider two cases.

@@

\textbf{case 2}: Participant $i$ can be selected when she departs and she misreports a cost $b_i$. If she still can not win the auction until she departs, she will get a payment equals $\frac{\tilde{f}^i_t(\mathbb{S}\backslash\{i\})}{\rho}$, which is the same as she bids truthfully because this payment has nothing to do with the bid. Otherwise, we assume she can win the auction at some time $t$ by misreporting lower cost (Apparently, higher cost doesn't ``help"). The participant's failure is due to two reasons: low efficiency or budget constraint. If it is because of the budget, she will still fails. If it is because the low efficiency, \ie, $\frac{\tilde{f}^i_t(\mathbb{S})}{c_i}\ge\rho$, we can derive $c_i \ge \frac{\tilde{f}^i_t(\mathbb{S})}{\rho}$. If she wins the auction and get a payment, this payment will be less than her cost. So we have proved this case.
